# Libraries

```{r}
library(xts)
library(stringr)
library(dygraphs)
```

# Constants

```{r}
DATASET.PATH <- 'Example_Option Time_and_sales ASHR 24082915.csv'
today <- as.Date('24-8-2015', format = '%d-%m-%Y')
```

## Loading the dataframe with the time and sales option data

```{r}

dataset <- read.csv(DATASET.PATH, header = FALSE, stringsAsFactors = FALSE, sep = ';')
dataset <- dataset[,-c(1,11)]
colnames(dataset) <- c('Time', 'Option', 'Quantity', 'Price', 'Exchange', 'Bid_X_Ask', 'Delta', 'Implied_Volatility_per_cent', 'Underlying')
```

The Option column must be splitted up since we have to distinguish the calls and puts options

```{r}
dataset$Type <- substr(dataset$Option, nchar(dataset$Option), nchar(dataset$Option))
dataset$Type <- ifelse(dataset$Type == 'C' , 'CALL', 'PUT')

dataset$Option <- substr(dataset$Option, 1, nchar(dataset$Option)-2)
```

Split up the Bid and ask in two columns

```{r}
split.bid.ask <- as.data.frame(do.call(rbind, sapply(dataset$Bid_X_Ask, USE.NAMES = FALSE, function(bid_ask){strsplit(bid_ask, 'x')})))
colnames(split.bid.ask) <- c('Bid', 'Ask')

dataset <- cbind(dataset, split.bid.ask)
dataset$Bid <- as.numeric(as.character(dataset$Bid))
dataset$Ask <- as.numeric(as.character(dataset$Ask))

dataset$Bid_X_Ask <- NULL
```

Removing the '%' in the values of the IV column
```{r}
dataset$Implied_Volatility_per_cent <- sub('%', '', dataset$Implied_Volatility_per_cent)
dataset[dataset$Implied_Volatility_per_cent == '--', c('Implied_Volatility_per_cent')] <- NA
dataset$Implied_Volatility_per_cent <- as.numeric(dataset$Implied_Volatility_per_cent)
```

## Change the types of the columns accordingly

Convert numeric types

```{r}
#Convert commas in points in the number before changing the type of the Quantity column
dataset$Quantity <- sapply(dataset$Quantity, function(element){
  ifelse(grepl(',', element), sub('[[:punct:]]', '', element), element)})

dataset$Quantity <- as.integer(dataset$Quantity)
```

Convert the Time variable in a xts type

```{r}
dataset$Time <- paste(today, dataset$Time, sep = ' ')
dataset <- xts(dataset, unique = FALSE, order.by = as.POSIXct(dataset$Time))
dataset$Time <- NULL
```

Change the order of the columns

```{r}
dataset <- dataset[,c('Option', 'Type', 'Quantity', 'Price', 'Bid', 'Ask',
                      'Implied_Volatility_per_cent', 'Delta', 'Underlying', 'Exchange')]
```

# TODO - Plot (dygraph) the timeseries (x axis) with the quantity of options (y axis)
#        divided by calls and puts hitting the ask and bid

