# Libraries

```{r}
library(xts)
```

Loading the dataframe with the time and sales option data

```{r}
DATASET.PATH <- 'Example_Option Time_and_sales ASHR 24082915.csv'
dataset <- read.csv(DATASET.PATH, header = FALSE, stringsAsFactors = FALSE, sep = ';')
dataset <- dataset[,-c(1,11)]
colnames(dataset) <- c('Time', 'Option', 'Quantity', 'Price', 'Exchange', 'Bid_X_Ask', 'Delta', 'Implied_Volatility', 'Underlying')
```

The Option column must be splitted up since we have to distinguish the calls and puts options

```{r}
dataset$Type <- substr(dataset$Option, nchar(dataset$Option), nchar(dataset$Option))
dataset$Type <- ifelse(dataset$Type == 'C' , 'CALL', 'PUT')

dataset$Option <- substr(dataset$Option, 1, nchar(dataset$Option)-2)
```

Split up the Bid and ask in two columns

```{r}
split.bid.ask <- as.data.frame(do.call(rbind, sapply(dataset$Bid_X_Ask, USE.NAMES = FALSE, function(bid_ask){strsplit(bid_ask, 'x')})))
colnames(split.bid.ask) <- c('Bid', 'Ask')

dataset <- cbind(dataset, split.bid.ask)
dataset$Bid_X_Ask <- NULL
```

Convert the Time variable in a xts type

```{r}

```

Change the types of the columns accordingly

```{r}

```

# TODO - Change the order of the columns by importance
# Time, Option, Type, Quantity, Price, Bid, Ask, Implied_Volatility, Delta, Underlying, Exchange





